---
title: "Healthcare Lab"
author: "Elise Treit"
date: "7/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Health Expenditures vs Coverage
### Setting up the notebook
Goals of this notebook are to understand how healthcare coverage and spending are related in the United States

First: to set up the environment, we will be using the Here and Project Template packages

```{r}
#make sure necessary packages are installed
install.packages("here")
```
```{r}
library("here")

```
Reading the data in as data frames, first 2 lines were notes about the csv, needed to skip them
```{r}
coverage <- read.csv(file = here::here("healthcare-coverage.csv"), skip = 2, header = TRUE)
spending <- read.csv(file = here::here("healthcare-spending.csv"), skip = 2, header = TRUE)
```

### Question 1: Is there a relationship between healthcare coverage and healthcare spending in the United States?
Looking at the data using the head() function, it is clear that years covered in coverage (2013-2016) are quite different from spending (1991 - 2014).



```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
